Presentation: OPX

### 2022-08-03 Presentasjon/Presentasjon v3.Rmd
Presetnasjon endelig

## <br> Exploring three options
- 1. Reading PDFs <br>
Issue: Not always published as text
- 2. Webscraping from Proff.no <br>
Issue: Proff.no does not allow (automated) webscraping
- 3. Webscraping the Brønnøysund registry <br>
Issue: No API access, and access costs ~ NOK 500 000

#BYTTE UT MED 1 2 3

@@

## {data-background="Images/tenke.png" data-background-size=cover}

@@

>>>>

## <br> Exploring three options
1. Reading PDFs <br>
Issue: Not always published as text
2. Webscraping from Proff.no <br>
Issue: Proff.no does not allow (automated) webscraping
3. Webscraping the Brønnøysund registry <br>
Issue: No API access, and access costs ~ NOK 500 000

@@

## {data-background="Images/upbeat_and_happy.png" data-background-size=cover}

@@

## <br> <br> <br> The End
**Thank you for this opportunity!** <br> <br> <br>
- Questions?
